What Drives State-Sponsored Violence?: Evidence from Extreme Bounds Analysis and Ensemble Learning Models

### 2018-11-30 paper-killings/manuscript.tex
small update

One can also infer that authoritarian and mixed political regime are more likely to engage in mass violence than democratic countries, a result that is also supported by both the EBA and the specialised literature. The number of military personnel positively affects the likelihood of mass killings, yet this increase is counterbalanced by military expenditures. Together these results indicate that countries with large and poorly-funded armed forces have higher risks of mass violence.

@@

I estimate a set of additional regressions to assess the robustness of the main findings. In regard to EBA, I include 10 variants of the original model. They largely confirm the prior results. First, I varied the number of covariates included in each regression to 3 and 5 while keeping the $M$ set of 3 control variables. The results are the same as those of the main model, except that ethnic fractionalisation and Polity IV squared become marginally significant with a CDF(0) of about 0.88. Second, we place different restrictions on the variance inflation factor (VIF) to test whether multicollinearity is driving the results. The two models with different values of VIF are identical to the model reported here, while in the model with no VIF restriction ethnic fractionalisation again fails to meet the threshold by a very small margin.

>>>>

One can also infer that authoritarian and mixed political regimes are more likely to engage in mass violence than democratic countries, a result that is also supported by both the EBA and the specialised literature. The number of military personnel positively affects the likelihood of mass killings, yet this increase is counterbalanced by military expenditures. Taken together, these results indicate that countries with large and poorly-funded armed forces have higher risks of mass violence.

@@

% Add a footnote about Sala-i-Martin's claim that the sample is unbiased. 
I estimate a set of additional regressions to assess the robustness of the main findings. In regard to EBA, I include 10 variants of the original model. They largely confirm the prior results. First, I varied the number of covariates included in each regression to 3 and 5 while keeping the $M$ set of 3 control variables. The results are the same as those of the main model, except that ethnic fractionalisation and Polity IV squared become marginally significant with a CDF(0) of about 0.88. Second, I place different restrictions on the variance inflation factor (VIF) to test whether multicollinearity is driving the results. The two models with different values of VIF are identical to the model reported here, while in the model with no VIF restriction ethnic fractionalisation again fails to meet the threshold by a very small margin.
